\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-20 paper.tex
Modify definition of constraints.

% Math shortcuts :
\newcommand\real{\mathbb{R}}
\newcommand\p{\mathbf{p}}
\newcommand\gT{\tilde{g}^T}
\newcommand\g{\tilde{g}}
\newcommand\CS{\mathcal{C}}
\newcommand\dimCS{n_\mathbf{C}}
\newcommand\body{{\cal B}}
\newcommand\Sone{\mathbf{S}^1}
\newcommand\Sthree{\mathbf{S}^3}
\newcommand\conf{\mathbf{q}}
\newcommand\xx{\mathbf{x}} % \x already defined in the class
\newcommand\cost{C}
\newcommand\weight{W}
\newcommand\translation{\mathbf{t}}
%\newcommand\tcolli{t_{coll\ i}}
\newcommand\tcolli{\kappa_i}
\newcommand\po{\mathbf{P}}
\newcommand\Jf{\Phi}
\newcommand\kernel{\mbox{Ker }}
\newcommand\U{\mathbf{u}}

@@

\subsection{Constraints}

@@

The principle of the method is to compute a constraint on the backtracked 
free-configuration $\xx_{i}(\tcolli)$ to avoid the encountered collision $\xx_{i+1}
(\tcolli)$. To handle this, we introduce a one-dimensional constraint based on the 
orthogonal direction of the encountered collision.

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left).
\textcolor{blue}{
In any configuration $\conf$, let 
$\po_j^l(\conf)$ be the coordinates in the frame of $\body_l$ of $\po_c$ expressed the frame of $\body_j$.
Let $M_1(\conf) \in SE(3)$ (respectively $M_2(\conf) \in SE(3)$) denote the homogeneous transformation 
between frames of $\body_1$ (respectively $\body_2$) and the global frame.
Thus, $\po_2^1(\conf) = M_{1}^{-1} (\conf) M_2 (\conf)$.
}

\textcolor{blue}{
In configuration $\xx_{i}(\tcolli)$, let $\mathbf{u}$ be the unit vector 
linking the points $\po_1$ and $\po_2$ (Figure~\ref{contact-points} right):
$$
\U = \frac{\po_2^1(\xx_{i}(\tcolli)) - \po_1^1(\xx_{i}(\tcolli))}{\|\po_2^1(\xx_{i}(\tcolli)) - \po_1^1(\xx_{i}(\tcolli))\|}
$$
}

Notice that $\mathbf{u}$ is well defined since configuration 
$\xx_{i}(\tcolli)$ is collision-free.
\textcolor{blue}{
Let $g$ be the function representing the projection of $\overrightarrow{\po_1(\conf)\,\po_2(\conf)}$ on $\mathbf{u}$. $g$ is defined for any $\conf \in \CS$ to $\real$ by:
$$
g (\conf) = \left(\po_2^1(\conf) - \po_1^1(\conf) | \mathbf{u}\right)
$$
}
%which is calculated from the last collision-free path at abscissa $\tcolli$.

Let $f$ be the function defined from $\CS^{wp}$ to $\real$ by:
$$
f (\xx) = g(\xx (\tcolli))
$$
The constraint is defined for any path $\xx$ by:
\begin {equation}\label{eq:new-constraint}
f(\xx) - f(\xx_{i}) = 0.
\end {equation}
This constraint forces the configuration $\xx (\tcolli)$ to keep the same projection on $\mathbf{u}$ as in $\xx_i (\tcolli)$. Since this constraint is 
non-linear, we linearize it around $\xx_{i}$: 
$$
\frac{\partial f}{\partial \xx}(\xx_i)(\xx - \xx_i) = 0
$$
The linearization step is described in the following 
section. Then, a line is added in the constraint Jacobian matrix $\Jf_i$:
\begin {align*}
\Jf_{i+1} &= \left(\begin{array}{c}L_1 \\ \vdots \\ L_{j+1}\end{array}\right)\ \mbox {with}\\
L_{j+1} &= \frac{\partial f}{\partial \xx}(\xx_i)
\end{align*}
\textcolor{blue}{This step is denoted by the function \texttt{addCollisionConstraint}}.

>>>>

% Math shortcuts :
\newcommand\real{\mathbb{R}}
\newcommand\p{\mathbf{p}}
\newcommand\gT{\tilde{g}^T}
\newcommand\g{\tilde{g}}
\newcommand\CS{\mathcal{C}}
\newcommand\dimCS{n_\mathbf{C}}
\newcommand\body{{\cal B}}
\newcommand\Sone{\mathbf{S}^1}
\newcommand\Sthree{\mathbf{S}^3}
\newcommand\conf{\mathbf{q}}
\newcommand\xx{\mathbf{x}} % \x already defined in the class
\newcommand\cost{C}
\newcommand\weight{W}
\newcommand\translation{\mathbf{t}}
%\newcommand\tcolli{t_{coll\ i}}
\newcommand\tcolli{\kappa_i}
\newcommand\po{\mathbf{P}}
\newcommand\Jf{\Phi}
\newcommand\kernel{\mbox{Ker }}
\newcommand\U{\mathbf{u}}
\newcommand\rotation{R}

@@

\subsection{Linear Constraints}

@@

The principle of the method is to compute a \textcolor{blue}{linear} constraint on the initialized on the 
free-configuration $\xx_{i}(\tcolli)$ to avoid the encountered collision $\xx_{i+1}
(\tcolli)$. To handle this, we introduce a one-dimensional constraint based on the 
orthogonal direction of the encountered collision.

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left).
\textcolor{red}{We denote by
  \begin{itemize}
  \item $\po_1$ (resp. $\po_2$) the point belonging to body $\body_1$ (resp. $\body_2$) that coincides with $\po_c$ in configuration $\xx_{i+1}(\tcolli)$,
  \item $M_1(\conf) \in SE(3)$ (resp. $M_2(\conf) \in SE(3)$) the rigid-body transformation representing the position of $\body_1$ (resp. $\body_2$) in the global frame in configuration $\conf$,
  \item $\rotation_1(\conf) \in SO(3)$ (resp. $\rotation_2(\conf) \in SO(3)$) the rotation associated with $M_1(\conf)$ (resp. $M_2(\conf)$).
  \end{itemize}
  The position of $\po_1$ (resp. $\po_2$) in the global reference frame depends on the configuration $\conf$ of the robot. We therefore denote $\po_1(\conf)$ (resp. $\po_2(\conf)$) this position.
We define $\U$ as the unit vector attached to $\body_1$, linking points $\po_1$ and $\po_2$ in configuration $\xx_{i}(\tcolli)$ (Figure~\ref{contact-points} right):
$$
\U (\conf) = \rotation_1(\conf)\rotation_1^{T}(\xx_{i}(\tcolli))\frac{\po_2(\xx_{i}(\tcolli)) - \po_1(\xx_{i}(\tcolli))}{\|\po_2(\xx_{i}(\tcolli)) - \po_1(\xx_{i}(\tcolli))\|}
$$
Note that
\begin{itemize}
\item $\U$ depends on the configuration of the robot $\conf$, since $\U$ moves with $\body_1$,
\item $\U$ is well defined since configuration $\xx_{i}(\tcolli)$ is collision-free.
\end{itemize}
}
\textcolor{blue}{
Let $g$ be the function mapping the projection of vector $\overrightarrow{\po_1\,\po_2}$ on $\mathbf{u}$ to a configuration $\conf$ . For any $\conf \in \CS$:
$$
g (\conf) = \left(\po_2(\conf) - \po_1(\conf) | \mathbf{u}\right)
$$
}
%which is calculated from the last collision-free path at abscissa $\tcolli$.

Let $f$ be the function defined from $\CS^{wp}$ to $\real$ by:
$$
f (\xx) = g(\xx (\tcolli))
$$
The constraint defined for any path $\xx$ by:
\begin {equation}\label{eq:new-constraint}
f(\xx) - f(\xx_{i}) = 0.
\end {equation}
aims at keeping colliding points $P_1$ and $P_2$ in configuration $\xx_{i+1} (\tcolli)$ apart in direction $\U$ defined by those points in configuration $\xx_{i} (\tcolli)$.
We linearize the constraint around $\xx_{i}$: 
$$
\frac{\partial f}{\partial \xx}(\xx_i)(\xx - \xx_i) = 0
$$
The computation of the linearized constraint is described in the next
section. Then, a line is added in the constraint Jacobian matrix $\Jf_i$:
\begin {align*}
\Jf_{i+1} &= \left(\begin{array}{c}L_1 \\ \vdots \\ L_{j+1}\end{array}\right)\ \mbox {with}\\
L_{j+1} &= \frac{\partial f}{\partial \xx}(\xx_i)
\end{align*}
\textcolor{blue}{This step is denoted by the function \texttt{addCollisionConstraint}}.
